Supervised Reinforcement Learning with Partial States: \\ a Teaching Method for Action Selection for HRI

### 2017-07-21 paper.tex
Update future work

This method still has to be tested in a real Human-Robot Interaction, and this
evaluation is currently being implemented and will be tested in a near future.

The current work could be extended to allow the agent continue to improve its
behaviour even in the absence of supervisor, progressively exploring around a learnt policy
improving its policy beyond what have been taught. This
could be done by allowing the supervisor to provide rewards during the learning
phase, and combine these rewards with the demonstrations to learn a reward
function in a fashion similar to Inverse Reinforcement Learning
\cite{abbeel2004apprenticeship}. These could also use partial states associated
to these rewards to have a general reward function despite a low number of
datapoints.
But without the supervisor, the assumption that only a
myopic action selection is sufficient would not hold anymore and the problem of
delayed rewards would have to be tackled.
%===============================================================================
%\section{Conclusion}
\label{sec:conclusion}
%==============================================================================
\section{Acknowledgments}
This work was supported by the EU FP7 DREAM project (grant no.  611391) and EU
H2020 Marie Sklodowska-Curie Actions project DoRoThy (grant 657227).

>>>>

The system presented in the previous section will be improved and
evaluated in the real world with children in the next months.

The current work could also be extended to allow the agent continue to improve its
behaviour even in the absence of supervisor, progressively exploring around the
learnt policy improving its behaviour beyond the demonstrations. This
could be done by allowing the supervisor to provide rewards during the learning
phase, and combine these rewards with the demonstrations to learn a reward
function in a fashion similar to Inverse Reinforcement Learning
\cite{abbeel2004apprenticeship}. These could also use partial states associated
to these rewards to ease the generalisation of the reward function with only a
low number of datapoints.
But without the supervisor, the assumption that only a
myopic action selection is sufficient would not hold anymore and the problem of
delayed rewards would have to be tackled.
%===============================================================================
%\section{Conclusion}
\label{sec:conclusion}
%==============================================================================
\section{Acknowledgments}
This work was supported by the EU FP7 DREAM project (grant no.  611391) and EU
H2020 Marie Sklodowska-Curie Actions project DoRoThy (grant 657227).
